Reionization Planck 2018 ...

### 2020-10-22 paper/rei.tex
Updates from Overleaf

\author{Chen Heinrich}\email{chenhe@caltech.edu}
\affiliation{$Jet\ Propulsion\ Laboratory,\ California\ Institute\ of\ Technology,\ Pasadena,\ California\ 91109,\ USA$}
\affiliation{$California\ Institute\ of\ Technology,\ Pasadena,\ California\ 91109,\ USA$}

@@

The paper is structured as follows. We first describe in section~\ref{sec:background} the background on the reionization principal components and the kernel density estimate (KDE) technique used for building the effective likelihood. Then in section~\ref{sec:results}, we describe the PC results using the Planck 2018 + \textsc{srollv2} likelihood, and compare with previous results in literature. Then in section~\ref{sec:effective_likelihood}, we present the effective likelihood code, and demonstrate its fidelity with two examples, 1) the standard steplike model, and 2) a two-parameter model where a plateau of ionization at high-$z$ is added to the standard one-step model for illustration purposes. Finally, we summarize our results and conclude in section~\ref{sec:conclusion}.

\section{Background}
\label{sec:background}

The principal component technique for constraining reionization using the large-angle $C_\ell^{EE}$ polarization spectrum was first introduced in Ref.~\cite{Hu:2003gh}. We now briefly summarize the PC technique in section~\ref{sec:PC}, as well as the kernel density estimate technique for building the effective likelihood in section~\ref{sec:KDE}. We refer the readers to Refs.~\cite{Hu:2003gh, Mortonson:2008rx, Mortonson:2007hq, Heinrich:2018btc}[pick 1-2] and Refs.~\cite{Heinrich:2016ojb} respectively for a more complete description on these topics.

\subsection{Reionization Principal Components}
\label{sec:PC}

We begin by parametrizing $x_e(z)$, the ionization fraction relative to the fully ionized hydrogen at redshift $z$, into its principal components $S_{a}(z)$ with respect to the CMB $E$-mode polarization:
%
\begin{equation}
x_e(z)=\xef(z)+\sum_{a}m_{a}S_{a}(z),
\label{eq:mmutoxe}
\end{equation}
%
where $m_a$ are the PC amplitudes and $\xef(z)$ is the fiducial model. We obtain the PCs $S_{a}(z)$ as eigenfunctions of the Fisher information matrix for $x_e(z)$ in a given range $z_{\rm min}<z<z_{\rm max}$ from cosmic variance limited $C_\ell^{EE}$ measurements 
%
\beq
F_{ij} = \sum_l \frac{1}{\sigma_l^2} \frac{\partial C_l^{EE}}{\partial x_e(z_i)}\frac{\partial C_l^{EE}}{\partial x_e(z_j)} = \sum_a S_a(z_i) \sigma_a^{-2} S_a(z_j),
\eeq
%
where we have discretized the redshift space with $\delta z= 0.25$, and where $\sigma_a^2$ are the variances of the PCs. We have rank-ordered the PCs from low to high variance, so that for the range $z_{min} = 6$ (to be consistent with Ly$\alpha$ forest constraints, e.g. \cite{Becker:2015lua}) and $z_{\rm max} = 30$, only the first 5 components are needed to describe all the information on $x_e$ carried by $C_\ell^{EE}$ to cosmic variance limit. In the work that follows, we therefore truncate the sum at $a = 1 .. n_{\rm{PC}}$, where $n_{\rm{PC}} = 5$ for $z_{\rm max} = 30$ and $n_{\rm{PC}} = 7$ for $z_{\rm max} = 50$.

Note that the $n_{\rm PC}$ PCs are a complete representation of the \textit{observable impact} of $x_e(z)$ on the $C_\ell^{EE}$, rather than the ionization history itself. In other words, 
given any $x_e^{\rm true}(z)$, we can project it onto the $n_{\rm PC}$ PC basis through
\begin{equation}
m_{a}=
  \int _{\zmin}^{\zmax} dz\, \frac{S_{a}(z) [x_e^{\rm true}(z)-\xef(z)]}{\zmax-\zmin},
\label{eq:xetommu}
\end{equation}
%
where the reconstructed $x_e(z)$ through Eq.~(\ref{eq:mmutoxe}) with truncated PCs will not reproduce the true ionization history $x_e(z) \neq x_e^{\rm true}(z)$, but rather it is the observed $C_\ell^{EE}$ that is reproduced to cosmic variance precision. We reiterate therefore, that the PC analysis is not a tool for reconstructing the ionization history from observations, but rather a forward-modeling tool which, by reducing the dimensionality of the model space to $n_{\rm PC}$, allows us to constrain all possible ionization histories between $z_{\rm min}<z<z_{\rm max}$ in a single analysis.

[rephrase this paragraph:]
``For the Planck data set, most of the information in the ionization history is carried by the
first two modes and therefore relates to the amount of high vs.~low redshift optical depth. We keep all 5 PCs  for completeness in representing the observable
impact of a given ionization history and to marginalize uncertainties that they introduce."

We follow Ref.~\cite{Heinrich:2018btc} to compute the CMB power spectra with PCs using a modified version of CAMB\footnote{CAMB: \url{http://camb.info}}~\cite{Lewis:1999bs, Howlett:2012mh}, where the PCs were discretized at $\delta z = 0.25$, and computed at the fiducial model $x_e^{\rm fid} = 0.15$. Note that following Ref.~\cite{Heinrich:2018btc}, we have updated the $\zmax = 30$ PCs to be computed with Planck 2015 rather than WMAP best-fit parameters, which results in minor differences between the PC functions used in Ref.~\cite{Heinrich:2016ojb} and here. For $z<6$, we follow camb to assume fully ionized hydrogen and singly ionized helium and for $z\leq 3.5$~\cite{Becker:2010cu}, doubly ionized helium~\cite{Becker:2010cu} with a width  $\Delta z = 0.5$.

We also put constraints on the cumulative Thomson optical depth derived parameters 
\begin{equation}
\tau(z,z_{\rm max}) = n_{\rm H}(0) \sigma_T \int_z^{z_{\rm max}} dz \frac{x_e(z) (1+z)^{2} }{H(z)},
\label{eq:cumtau}
\end{equation}
where $n_{\rm H}(0)$ is the hydrogen number density at $z=0$, $\sigma_T$ is the Thomson scattering cross-section and $H(z)$ is the Hubble parameter. Because the optical depth is more directly related to the CMB observables than the ionization history itself, it allows us to make meaningful comparisons between the PC results and those with a specific prior in model space such as those admitting a particular functional form.

For example, the standard steplike model adopted in CAMB uses a tanh function to parameterize the hydrogen and singly ionized helium reionization
 \begin{equation}
x_e^{\rm true}(z) = \frac{1+f_{\rm He}}{2}\left\{  1+ \tanh\left[ \frac{y(z_*)-y(z)}{\Delta y} \right] \right\},
 \label{eqn:tanh}
 \end{equation}
 where $y(z)=(1+z)^{3/2}$, $\Delta y=(3/2)(1+z)^{1/2}\Delta z$, and $\Delta z = 0.5$,
and has an implicit prior in model space that excludes finite ionization above its transition redshift.

The PCs on the other hand, allow for arbitrary values of $x_e(z)$ when no prior constraints on the mode amplitudes $m_a$ are imposed. When showing results, however, we do impose a physicality prior derived from the condition $0<x_e<x_e^{\rm max}$ following Ref.~\cite{Mortonson:2008rx}
%
\begin{equation}
\sum_{a=1}^5 m_a^2 \le (x_e^{\rm max}-x_e^{\rm fid})^2,
\end{equation}
where $x_e^{\rm fid}=0.15$ and $m_a^{-} \le m_a \le m_a^{+}$ with
\begin{equation}
m_a^{\pm} = \int_{z_{\rm min}}^{z_{\rm max} } dz \frac{S_a(z)[x_e^{\rm max} -2 x_e^{\rm fid}(z)]
\pm x_e^{\rm max} | S_a(z)|}{2(z_{\rm max}-z_{\rm min})}.
\label{eq:individualprior}
\end{equation}
%
Note that the original $0<x_e<x_e^{\rm max}$ condition cannot be strictly enforced here because we do not keep all but the first $n_{\rm PC}$ PCs, so these priors in $m_a$ are necessary but not sufficient conditions for physicality. They are however noninformative priors when the PC constraints are being used for evaluating the likelihood of a series of physical models, which we will now describe in the next section.

%we employ the smoothed $x_e$ which formally has support beyond the bounds. 
% We include this small correction by integrating
% slightly past $z_{\rm max}$ in practice.  Here $n_{\rm H}(0)$ is the hydrogen number density at $z=0$.
   %Consequently we smooth the ionization history in Eq.~(\ref{eq:mmutoxe}) with a 
%Gaussian in $\mathrm{ln}(1+z)$ of width $\sigma_{\mathrm{ln}(1+z)} = 0.015$.

\subsection{Effective Likelihood from PCs -- Kernel Density Estimate}
\label{sec:KDE}

The completeness property of the PCs enables us to turn PC chains obtained from a MCMC run into an effective likelihood. In the following, we briefly recap the kernel density estimate technique used to build this likelihood and refer the readers to Ref.~\cite{Heinrich:2016ojb} for more details.

The PC chains are composed of $N_{\rm sample}$ samples of discrete values of $\mathbf{m}_i = \{m_1, \ldots, m_5\}$ along with multiplicities $w_i$ for $i = 1$...$N_{\rm sample}$. Given any physical ionization history $x_e(z)$, we first obtain its PC representation $\mathbf{m}$ using Eq.~\ref{eq:xetommu}. Since $\mathbf{m}$ could take any continuous value, we approximate its effective likelihood with a kernel density estimate
\beq
{\cal L}_{\rm PC}\left({\rm data}|\mathbf{m} \right)  = \sum_{i = 1}^{N_{\rm sample}} w_i K_f(\mathbf{m}-\mathbf{m}_i),
\eeq
where the overall normalization is arbitrary, and where we have chosen the smoothing kernel $K_f$ to be a  multivariate Gaussian with mean zero and covariance $f\mathbf{C}$, where $\mathbf{C}$ is the $N_{\rm PC} \times N_{\rm PC}$ covariance matrix estimated from the PC chains (see Table~\ref{tab:PC_stats}) and $f$ is a fraction smaller than 1.

For a Gaussian posterior, increasing the covariance by $1+f$ corresponds to increasing the standard deviation by approximately $1+f/2$. To minimize the amount of smoothing needed while still maintaining good accuracy in the tail of the distribution for any physical models, we oversample the PC distributions by running the PC chains far beyond convergence for about $N_{\sample} \approx XX \times 10^{X}$ [to fill] chain samples. For this $N_{\sample}$, a fraction of $f = 0.14$ should be sufficient. Note also that we employ PC chains without the physicality priors allowing the smoothing kernel to cross over these priors.

Evaluating the posterior distribution of model parameters $\bf p$ using the effective likelihood
\begin{equation}
P({\bf p}| {\rm data}) \propto {\cal L}_{\rm PC}\left[ {\rm data}|\mathbf{m}(\bf p) \right] P(\bf p),
\end{equation}
we demonstrate a successful recovery of the posterior distributions from direct MCMC analyses (using the Planck likelihood and varying all cosmological parameters) with significantly less computational time. We show these results in sections~\ref{sec:example1} and~\ref{sec:example2} for two example models: the tanh model and a two-parameter model allowing for high-redshift ionization.

%Therefore, the PC-based effective likelihood allows one to easily explore different models of ionization history while providing a much faster convergence in the MCMC analysis.

%In what follows, we also show a even simpler effective likelihood, which approximates the $m_a$ posterior as a multivariate Gaussian with mean $\bar{\bf m}$ and covariance $\bf C$:
%\begin{equation}
% {\cal L}_{\rm gauss}\left({\rm data}|\mathbf{m} \right) = \frac{ e^{-\frac{1}{2} ({\bf m}-\bar{\bf m})^T {\bf C}^{-1} ({\bf m}-\bar{\bf m}) } }{\sqrt{(2\pi)^{N_{\rm PC}} | \mathbf{C}| }}.
% \label{eq:gaussian}
% \end{equation}
% This likelihood may suffice for models near the peak of the distribution, but would not be accurate for sampling less-constrained models or in the tails of distributions.

\section{Planck 2018 PC Results}
\label{sec:results}

We now present the complete reionization constraints obtained from the Planck 2018 likelihoods using the principle component technique.

\subsection{Constraints on Principle Components}

We use the official Planck likelihoods \textsc{plik\_lite} for the high-$\ell$ $TT$, $TE$ and $EE$ as well as \textsc{lowl} for the low-$\ell$ $TT$ throughout the paper. (We have tested that our results do not change when we switch to the full version \textsc{plik full} where the foregrounds are marginalized over in the likelihood.) For the low-$\ell$ $EE$, we use the third-party released \textsc{srollv2} likelihood for our official result. Compared to the official version released by Planck \textsc{lowE}, the new \textsc{srollv2} likelihood was made with an improved foreground cleaning method [cite], and leads to a factor of two improvement in $\tau$ in the steplike model. We will compare the PC results from these likelihoods later in this section.

[I'm here.]

In Fig.~\ref{fig:plot_mjs_2018_vs_2015}, we show the constraints in the $m_a-m_b$ plane of Planck 2015 vs Planck 2018. [Describe changes] [Mention Gaussian covariance]

\begin{itemize}
    \item compare with Planck 2015 our PC results; Fig.~\ref{fig:plot_mjs_2018_vs_2015} shows the PC constraints of Planck 2015 vs Planck 2018. [Describe changes] [Mention Gaussian covariance]
    \item insert table of mean and covariance matrix for the PC components?
    \item make a point that tanh misses high-z again, compare to PCs using the tau($>z$) plot tanh vs PCs.
    \item statement that zmax = 50 and zmax = 30 are consistent, there is no evidence for high-redshift ionization for $z>30$.\\
\end{itemize}

@@

\begin{itemize}
    \item compare with Planck official results
    \item comment that Planck tau(15,30) constraints are too stringent (flex knots). Compare to ours. Point out why.
    \item{ Comments on priors (see below).}
    \item (*maybe in  another section): make a point that dz = 0.5 for tanh may not be sufficient for experiments after Planck. This was for higher tau, so transition happens at higher redshift. Now tau is much lower.
\end{itemize}

@@

\begin{widetext}

\begin{figure}
\includegraphics[width=0.7\textwidth]{results/pc_results/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite.pdf}
\caption{Constraints from Planck data on the amplitudes of the five reionization principle components that describe all physical ionization models up to $z_{\rm max} = 30$. We show in red the Planck 2015 and the improved Planck 2018 contours in blue which uses the low-$\ell$ $EE$ likelihood \textsc{srollv2}. The 1D posterior distributions are shown on the diagonal and the 2D 68\% and 95\% C.L. regions in the $m_a-m_b$ planes in the lower triangle. The physicality priors on the ionization history used in this work are delineated by the box boundaries. [TODO: update legend]}
\label{fig:plot_mjs_2018_vs_2015}
\end{figure}

\end{widetext}

\begin{figure}
\includegraphics[width=0.4\textwidth]{results/pc_results/plot_m1_m2_pl18_pc_zmax30_pliklite_srollv2_vs_pl18_pc_zmax30_pliklite_wTauTrajectory.pdf}
\caption{The best-constrained $z_{\rm max} = 30$ PC plane, $m_1-m_2$. We compare Planck 2018 results with two different low-$\ell$ $EE$ likelihoods: the official \textsc{lowE} likelihood vs. the third-party released \textsc{srollv2} likelihood (zoomed-in from Fig.~\ref{fig:plot_mjs_2018_vs_2015}). [Comments on shift m1-m2 plane]. [TODO: Add Gaussian covariance, add legend, shrink x-axis]
}
\label{fig:plot_m1m2}
\end{figure}

\begin{figure}
\includegraphics[width=0.4\textwidth]{results/pc_results/plot_m1_m2_pl18_pc_zmax30_pliklite_srollv2_vs_pl18_pc_zmax30_pliklite_wTauTrajectory.pdf}
\caption{[placeholder, maybe not] need m1-m2 plane for zmax = 30 using Planck 2018 vs 2015.
}
\label{fig:plot_m1m2}
\end{figure}

@@

>>>>

\author{Chen Heinrich}\email{chenhe@caltech.edu}
\affiliation{California Institute of Technology, Pasadena, California 91109, USA}
\affiliation{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, California 91109, USA}

@@

The paper is structured as follows. We first describe in section~\ref{sec:background} the background on the reionization principal components and the kernel density estimate (KDE) technique used for building the effective likelihood. Then in section~\ref{sec:results}, we describe the PC results using the Planck 2018 + \texttt{srollv2} likelihood, and k

In Fig.~\ref{fig:plot_m1m2_lowE_vs_srollv2} we also compare the Planck 2018 results with two different low-$\ell$ $EE$ likelihoods: \texttt{simall\_EE} and \texttt{srollv2}. The \texttt{srollv2} contours are shrunk nearly directly along the lines of constant optical depth $\tau$ ($\tau_{12} = \tau_1 m_1 + \tau_2 m_2$) [wanna show this]? [Might be nice to overlay the tanh trajectories, no 1 sigma, 2 sigma business].

\subsection{Implications for optical depth}

We continue the comparison in the space of cumulative optical depth $\tau(z, \zmax)$, which is a better quantity for visualizing and comparing PC results than the ionization history $x_e$ itself because of it is the quantity most closely related to observables. Recall that these truncated PCs provide only accurate descriptions of the models in terms of their \textit{observable} impact, and are not tools for reconstructing the precise ionization history.

In Fig.~\ref{fig:plot_taugtz_2015_vs_2018}, we compare the 68\% and 95\% confidence level contours in $\tau(z, \zmax)$ for the Planck 2015 (red regions) and the Planck 2018 results (solid lines).
...

In Fig.~\ref{fig:plot_taugtz_lowE_vs_srollv2}, we compare the Planck 2018 results with the two different low-$\ell$ $EE$ likelihoods. [Do we need this?]

In Fig.~\ref{fig:plot_taugtz_PC_vs_tanh}, we compare the PC results against the steplike model. It is clear that the tanh model does not allow for high redshift ionization by construction. The total optical depth allowed by the PC chains sampling the entire physical model space is actually slightly higher due to the contributions from these higher redshifts. [do we want PC version with the physicality priors actually?]\\

We show however, using a separate PC chains with $\zmax = 50$, that there is no evidence for optical depth at higher redshifts than 30. In Fig.~\ref{fig:plot_taugtz_zmax30_vs_zmax50}, we show that the contours in $\tau(z, \zmax)$ are consistent between the $\zmax = 30$ (red regions) and $\zmax = 50$ results (black lines), and that their total optical depth constraints are practically identical: 
\beq
\tau_{\rm PC,\, \zmax=30} = XX \pm XX,
\eeq
and
\beq
\tau_{\rm PC,\, \zmax=50} = XX \pm XX.
\eeq
We have an upper limit on $\tau(15, \zmax)$ of 
\beq
\tau(z, \zmax)_{\rm PC,\, \zmax=30} < XX \; (95\% \mathrm{CL})
\eeq
and 
\beq
\tau(z, \zmax)_{\rm PC,\, \zmax=50} < XX \; (95\% \mathrm{CL})
\eeq

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{[placeholder] PC chains for zmax = 30. Planck 2018 srollv2 likelihood vs Planck 2015).
}
\label{fig:plot_taugtz_2015_vs_2018}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{PC chains for zmax = 30. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:plot_taugtz_lowE_vs_srollv2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{PC zmax = 30 vs tanh chains with plik\_full\_TTTEEE for the high-l likelihood.
}
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{Comparing zmax = 30 and 50 PC chains using Planck 2018 original lowE likelihood (plik\_lite\_TTTEEE + lowl + sroll2\_EE). Note that the zmax = 30 uses 5 PCs, whereas the zmax = 50 chains uses 7 PCs. .
}
\label{fig:plot_taugtz_zmax30_vs_zmax50}
\end{figure}

@@

Outline
\begin{itemize}
    \item compare with Planck official results
    \item comment that Planck tau(15,30) constraints are too stringent (flex knots). Compare to ours. Point out why.
    \item{ Comments on priors (see below).}
    \item (*maybe in  another section): make a point that dz = 0.5 for tanh may not be sufficient for experiments after Planck. This was for higher tau, so transition happens at higher redshift. Now tau is much lower.
\end{itemize}

@@

@@

------ \textbf{Some Numbers} ------ \\

\textbf{Planck official results 2015, 2016, 2018} \\

\begin{itemize}

    \item Planck 2015 results (LFI): $\tau = 0.067 \pm 0.022$ (68\%) \\

    \item Planck 2016  intermediate results (LFI): $\tau = 0.055 \pm 0.009$ (68\%) \\

    \item Planck 2018 results: $\tau = 0.0506 \pm 0.0086$ (68\%) \\

\end{itemize}

\textbf{Planck 2018 paper} \\

Here lowE means lowE data only, fixing all other cosmological parameters including $A_s e^{-2\tau}$\\

\begin{itemize}

\item $\tau = 0.0519+0.0030-0.0079$ (lowE; flat $\tau$ prior; TANH)(68\%); \\

\item $\tau = 0.0504+0.0050
-0.0079$ (lowE; flat $\tau$ prior; FlexKnot)(68\%); \\

\item $\tau = 0.0487+0.0038
−0.0081$ (lowE; flat $\tau$ prior; PCA)(68\%).

\end{itemize}

\textbf{Upper limit on high-redshift optical depth} (only given for the FlexKnot method):

$\tau(15, 30) < 0.006$ (lowE, flat $\tau(15, 30)$, FlexKnot); \\

$\tau(15, 30) < 0.007$ (lowE, flat knot, FlexKnot).\\

Statements to address:

\begin{enumerate}
    \item {\textbf{Statement on prior in Planck 2018}:  ``Heinrich & Hu (2018) construct a prior that is uniform on τ, but which increases the allowed unphysical parameter space and is chosen a posteriori. Here we instead use the flat prior constructed by the procedure described in Millea & Bouchet (2018) and Handley & Millea (2019), which does not admit extra unphysical models and gives the most generic prior that leaves the prior on $\tau$ uniform."}

    \item {Is this statement on tanh in Planck 2018 paper correct?} `` The TANH result gives slightly higher optical depth than the others, which is primarily driven by the fixed duration of reionization assumed."} \\

    \item{\textbf{Other comments on our PC prior giving higher optical depth}: ``The PCA result is slightly lower, and is partly affected by the imperfect physicality priors that allow unphysical negative ionization fractions." and ``Millea \& Bouchet showed that the majority of this (2$\sigma$) preference disappeared when using the lower-noise Planck HFI SimLow likelihood (intermediate results reduction of systematics), with an additional sub-dominant effect due to the choice of prior."}

How likelihoods and systematics evolved over time:

\begin{enumerate}
    \item 
    \item {Planck 2018 paper attribute the 2018 upper limit on $\tau(15, 30)$ being \textbf{about 3 times more} stringent than the intermediate results by Millea \& Bouchet to the $SimLow \rightarrow SimAll$ where there was better control of systematics in HFI polarization.}
\end{enumerate}

[high redshift going away should be attributed to better control of systematics in HFI polarization data (changes in the SimAll likelihood compared to SimLow) [cite Planck 2018 results cp]]
